\paperTitle

### 2014-01-31 doc/icml2014/directed.tex
move examples

% DONE: too wordy
%\section{Consistent Parameter Estimation in Directed Models}
\section{Directed models}
\label{sec:directed}

@@

\begin{figure}
  \centering
  \input{figures/grid-outline.tikz}
  \caption{A directed grid model.}
  \label{fig:grid}
\end{figure}

Consider the directed grid model shown in \figureref{grid} which
  % DONE: all the different dependency => too strong
  captures the local dependency structures possible in
  a Bayesian network.
The model has eight observed variables $x^a_1, x^b_1 \cdots, x^a_4, x^b_4$ and four
  hidden variables $h_1, \cdots, h_4$.
The parameters of this model are the conditional probability tables
$\pi \eqdef \Pr(h_1) \in \Re^k, T \eqdef \Pr(h_2 | h_1) = \Pr(h_3 | h_1) \in \Re^{k \times k},
V \eqdef \Pr(h_4 | h_2, h_3) \in \Re^{k \times k \times k}$ and $O \eqdef \Pr(x^a_i | h_i)
=  \Pr(x^b_i | h_i) \in \Re^{d \times k}$. 
Finally, we assume $O$ and $T$ have full column rank.

@@

>>>>

% DONE: too wordy
%\section{Consistent Parameter Estimation in Directed Models}
\section{Directed models and exclusive views}
\label{sec:directed}

@@

%\begin{figure}
%  \centering
%  \input{figures/grid-outline.tikz}
%  \caption{A directed grid model.}
%  \label{fig:grid}
%\end{figure}

%Consider the directed grid model shown in \figureref{grid} which
Consider the directed grid model shown in \figureref{approach}(a) which
  % DONE: all the different dependency => too strong
  captures the local dependency structures possible in
  a Bayesian network.
The model has eight observed variables $x^a_1, x^b_1 \cdots, x^a_4, x^b_4$ and four
  hidden variables $h_1, \cdots, h_4$.
The parameters of this model are the conditional probability tables
$\pi \eqdef \Pr(h_1) \in \Re^k, T \eqdef \Pr(h_2 | h_1) = \Pr(h_3 | h_1) \in \Re^{k \times k},
V \eqdef \Pr(h_4 | h_2, h_3) \in \Re^{k \times k \times k}$ and $O \eqdef \Pr(x^a_i | h_i)
=  \Pr(x^b_i | h_i) \in \Re^{d \times k}$. 
Finally, we assume $O$ and $T$ have full column rank.

@@

\begin{figure}
  \centering
  \subfigure[Hidden Markov Model] {
    \includegraphics[width=0.45\columnwidth]{figures/hmm.pdf}
    \label{fig:examples-hmm}
  }
%  \subfigure[Directed grid model] {
%    \label{fig:examples-grid}
%    \includegraphics{figures/grid.pdf}
%  }
  \subfigure[Tree model] {
    \includegraphics[width=0.45\columnwidth]{figures/tree.pdf}
    \label{fig:examples-tree}
  }
  \caption{Additional examples of models learnable using \LearnMarginals}
  \label{fig:examples}
\end{figure}

\paragraph{Hidden Markov Model}

In this example (\figureref{examples-hmm}), we assume that
  $\Pr(x_i|h_i) = O  ~\forall i$  and that $\Pr(h_{i+1} | h_i)
  = T ~\forall i$ (i.e. we have parameter sharing).
Note that while the first (and last) hidden variables $h_1, h_T$ in the
  sequence are not bottlenecks, they still have exclusive views ($x_1$ and
  $x_T$ respectively) whose parameters we know because they share
  parameters, $O$.
In step 1 of our algorithm, we use the bottleneck $h_2$ with views $x_1,
  x_2, x_3$ and solve $O$.
In step 2 of our algorithm, we can recover $\pi$ by solving for the
  unary clique $\{h_1\}$ and recover $T$ from the clique $\{h_{1},
  h_{2}\}$.

\paragraph{Latent Tree Structure}

In the latent tree structure (\figureref{examples-tree}), let the
  parameters be $\Pr(h_i) = \pi$, $\Pr(h_i | h_1) = T ~i \in \{2,3,4\}$
  and $\Pr(x^a_i | h_i) = \Pr(x^b_i | h_i) = O ~i \in \{2,3,4\}$.
Note that while $h_1$ is not directly connected to an observed variable,
  it is still a bottleneck, with views $x^a_2, x^a_3, x^a_4$.

In step 1, we recover the parameters $O$ from the bottleneck $h_2$ with
  views $\{x^a_2, x^b_2, x^a_3\}$. We also recover the conditional moments
  $\mOpp{2}{1}$, $\mOpp{3}{1}$, $\mOpp{4}{1}$ for $h_1$. 
In step 2, we can recover $\pi$ from the clique $\{h_1\}$, using any
  one of views (they are all exclusive). 
To recover $T$ from the clique $\{h_1, h_2\}$, we use the views $x^a_2$
  (exclusive to $h_2$) and $x^a_3$ (exclusive to $h_3$). Note that while
  $x^a_3$ is also a view for $h_2$, $x^a_3$ is independent of $h_2$ given
  $h_1$.

### 2014-01-31 doc/icml2014/examples.tex
move examples

\subsection{More examples}

We will now instantiate our algorithm for a couple more examples, illustrated in \figureref{examples}.

\begin{figure}
  \centering
  \subfigure[Hidden Markov Model] {
    \includegraphics[width=0.45\columnwidth]{figures/hmm.pdf}
    \label{fig:examples-hmm}
  }
%  \subfigure[Directed grid model] {
%    \label{fig:examples-grid}
%    \includegraphics{figures/grid.pdf}
%  }
  \subfigure[Tree model] {
    \includegraphics[width=0.45\columnwidth]{figures/tree.pdf}
    \label{fig:examples-tree}
  }
  \caption{Additional examples of models learnable using \LearnMarginals}
  \label{fig:examples}
\end{figure}

\paragraph{Hidden Markov Model}

In this example (\figureref{examples-hmm}), we assume that
  $\Pr(x_i|h_i) = O  ~\forall i$  and that $\Pr(h_{i+1} | h_i)
  = T ~\forall i$ (i.e. we have parameter sharing).
Note that while the first (and last) hidden variables $h_1, h_T$ in the
  sequence are not bottlenecks, they still have exclusive views ($x_1$ and
  $x_T$ respectively) whose parameters we know because they share
  parameters, $O$.
In step 1 of our algorithm, we use the bottleneck $h_2$ with views $x_1,
  x_2, x_3$ and solve $O$.
In step 2 of our algorithm, we can recover $\pi$ by solving for the
  unary clique $\{h_1\}$ and recover $T$ from the clique $\{h_{1},
  h_{2}\}$.

\paragraph{Latent Tree Structure}

In the latent tree structure (\figureref{examples-tree}), let the
  parameters be $\Pr(h_i) = \pi$, $\Pr(h_i | h_1) = T ~i \in \{2,3,4\}$
  and $\Pr(x^a_i | h_i) = \Pr(x^b_i | h_i) = O ~i \in \{2,3,4\}$.
Note that while $h_1$ is not directly connected to an observed variable,
  it is still a bottleneck, with views $x^a_2, x^a_3, x^a_4$.

In step 1, we recover the parameters $O$ from the bottleneck $h_2$ with
  views $\{x^a_2, x^b_2, x^a_3\}$. We also recover the conditional moments
  $\mOpp{2}{1}$, $\mOpp{3}{1}$, $\mOpp{4}{1}$ for $h_1$. 
In step 2, we can recover $\pi$ from the clique $\{h_1\}$, using any
  one of views (they are all exclusive). 
To recover $T$ from the clique $\{h_1, h_2\}$, we use the views $x^a_2$
  (exclusive to $h_2$) and $x^a_3$ (exclusive to $h_3$). Note that while
  $x^a_3$ is also a view for $h_2$, $x^a_3$ is independent of $h_2$ given
  $h_1$.

>>>>

%\subsection{More examples}

%We will now instantiate our algorithm for a couple more examples, illustrated in \figureref{examples}.
